cardinalR: Generating interesting high-dimensional data structures

### 2025-04-30 paper-cardinalR.Rmd
Updated polynomial_tb
Updated cube_tb

```{r}
cube_tb <- tibble(fun = c("gen_gridcube",
                          "gen_unifcube",
                          "gen_cubehole"), 
                      exp = c("",
                              "", 
                              ""))
```

@@

```{r}
polynomial_tb <- tibble(fun = c("gen_quadratic",
                                "gen_cubic"), 
                        exp = c("",
                                ""))
```

>>>>

```{r}
cube_tb <- tibble(fun = c("gen_gridcube",
                          "gen_unifcube",
                          "gen_cubehole"), 
                      exp = c("Generate a cube with specified grid points along each axes.",
                              "Generate a cube with uniform points.", 
                              "Generate a cube with a hole."))
```

@@

```{r}
polynomial_tb <- tibble(fun = c("gen_quadratic",
                                "gen_cubic"), 
                        exp = c("Generate a quadratic pattern.",
                                "Generate a cubic pattern."))
```
